On Secure Delegation of SampBQP with a Classical Client

### 2020-02-01 bqp.tex
Fix typos

\begin{thm}
	Let $n$ be large enough to achieve negligible completeness and soundness for the corresponding $\QMA$ certificate checks.
	Then \protoref{proto:BQP} is a $\QPIP_1$ and constant round protocol for $\BQP$ with negligible completeness and soundness.
\end{thm}

@@

\begin{thm}
	Let $n$ be large enough to achieve negligible completeness and soundness for the corresponding $\QMA$ certificate checks.
	Let $\lambda$ be the security parameter.
	Then \protoref{proto:BlindBQP} is a $\QPIP_1$, constant round, and IND-CPA protocol for $\BQP$ with negligible completeness and soundness.
\end{thm}
\begin{proof}
	I promise this is true...
\end{proof}

>>>>

\begin{thm}
	Let $n$ be large enough to achieve negligible completeness and soundness for the corresponding $\QMA$ certificate checks.
	Then \protoref{BQP} is a $\QPIP_1$ and constant round protocol for $\BQP$ with negligible completeness and soundness.
\end{thm}

@@

\begin{thm}
	Let $n$ be large enough to achieve negligible completeness and soundness for the corresponding $\QMA$ certificate checks.
	Let $\lambda$ be the security parameter.
	Then \protoref{BlindBQP} is a $\QPIP_1$, constant round, and IND-CPA protocol for $\BQP$ with negligible completeness and soundness.
\end{thm}
\begin{proof}
	I promise this is true...
\end{proof}
